### 2024-11-11 README.Rmd
unit tests: embeddings

```{r, eval=FALSE}
# function that takes character vector and outputs data frame
sbert_embeddings <- function(texts) {
	text::textEmbed(
	  texts,
	  model = "sentence-transformers/all-MiniLM-L12-v2", # model name
	  layers = -2,  # second to last layer (default)
	  tokens_select = "[CLS]", # use only [CLS] token
	  dim_name = FALSE,
	  keep_token_embeddings = FALSE
  )$texts[[1]]
}

>>>>

```{r, eval=FALSE}
# function that takes character vector and outputs a data frame
sbert_embeddings <- function(texts) {
	text::textEmbed(
	  texts,
	  model = "sentence-transformers/all-MiniLM-L12-v2", # model name
	  layers = -2,  # second to last layer (default)
	  tokens_select = "[CLS]", # use only [CLS] token
	  dim_name = FALSE,
	  keep_token_embeddings = FALSE
  )$texts[[1]]
}
